TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-20 paper/paper.tex
-

The results have shown that the current default TCP congestion control algorithms are showing a fair behavior: The bandwidth is allocated equally among all nodes. Therefore, currently no traffic control is needed, unless someone would create an unfair TCP congestion control algorithm. This can, after more research, be detected by one of the monitoring solutions proposed in this paper. As for the tested TCP congestion control algorithms, there is no impact on the service and availability for customers when using those algorithms mixed in one environment.

@@

% For reference, from the proposal:

Our main research question is:
{\it How can a datacenter provide an reliable and performant environment for
customers when multiple TCP congestion control algorithms are used in the
network?}

\vspace{0.5cm}

This main research question divides in five sub-questions:

\begin{enumerate}
	\item What TCP congestion algorithms are most commonly implemented?
	\item How do these TCP congestion algorithms work?
	\item How do these TCP congestion algorithms differ in behavior?
	\item What is the impact on the availability and service for customers when using different, competing congestion algorithms?
	\item What measures could be taken to split bandwidth equally among tenants?
\end{enumerate}

>>>>

The results have shown that the current default TCP congestion control algorithms are showing fair behavior: The bandwidth is allocated equally among all nodes. Therefore, currently no traffic control is needed, unless someone would create an unfair TCP congestion control algorithm. This can, after more research, be detected by one of the monitoring solutions proposed in this paper. As for the tested TCP congestion control algorithms, there is no impact on the service and availability for customers when using those algorithms mixed in one environment.

@@
